\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{babel}

\begin{document}

\title{True Statements.}
\maketitle

\begin{enumerate}
    \item Na$_3$Bi is a natural Dirac semimetal formed from band inversion.
    
    \item It is a hexagonal crystalline system with a unit cell that contains 8 atoms. 6 of them are Na and 2 are Bi.
    
    \item This crystal has symmetries represented by the P$6_3$/mmc space group.  
    
    \item In particular, this crystal has time-reversal and inversion symmetries as well as $C_3$ symmetry about the z-axis. 
    
    \item $C_3$ symmetry corresponds to operations rotating the crystal structure by 2 $\pi$/3.
        
    \item Additionally, Na$_3$B has strong spin-orbit coupling.
    
    \item Na$_3$Bi has 2 Dirac points along the $k_z$ axis at non-time-reversal invariant momenta away from $k_z = 0$.
    
    \item There are protected surface states of Fermi arcs on the (100) and (110) plane for momentum $k_z = 0$.  
    
    \item The momentum $k_z = 0$ for the (100) and (110) planes has $\nu = 1$, which signifies a quantum spin hall insulating state.  
    
    \item The rotation symmetry that prevents the Dirac points from being gapped out is $C_3$ symmetry about the z-axis.
    
    \item Near the Fermi level and around the $\Gamma$ point, the Na $3s$ orbitals comprise the conduction band while the valence band is composed of Bi $6p_x,p_y,p_z$ orbitals.
    
    \item Fermi arcs are surface states that connect the momentum space surface projections of the bulk Weyl points. 
    
    \item Along surfaces whose surface normals are along the z-axis, the Dirac points and the Fermi arcs project onto a single Dirac point.
    
\end{enumerate}

\end{document}